Figure 2 - Overview heatmaps for IP-MS and ChIP

### 2024-08-06 ms_figure_2_overview-heatmaps.Rmd
reorder panels in Supplementary Fig2 and adjust whitespace

cowplot::plot_grid(
    gg_enrpairs,
    cowplot::plot_grid(
        hm_ipms_hot,
        gg_rnaviolin,
        ggpca2,
        ggpca3,
        ncol = 1,
        rel_heights = c(1.25, 0.75, 1.1, 0.9),
        labels = c("", "C", "D", "E")
    ),
    rel_widths = c(1, 0.65), 
    scale = 0.9, nrow = 1,
    labels = c("A", "B")
)
```

>>>>

cowplot::plot_grid(
    cowplot::plot_grid(
        ggpca2,
        ggpca3,
        cowplot::plot_grid(NULL, gg_rnaviolin, ncol = 1,
                           rel_heights = c(0.1, 0.9)),
        cowplot::plot_grid(NULL, hm_ipms_hot, ncol = 1,
                           rel_heights = c(0.1, 0.9)),
        ncol = 1,
        rel_heights = c(1.1, 0.9, 0.8, 1.2),
        labels = c("", "", "C", "D")
    ),
    gg_enrpairs,
    rel_widths = c(0.65, 1), 
    scale = 0.9, nrow = 1,
    labels = c("A", "B")
)
```
